The \dealii{} Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Unify typesetting of deal.II

\title{The \dealii Library, Version 9.2}

@@

\dealii version 9.2.0 was released May XYZ, 2020.
\todo[inline]{Need to update date.}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.2. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

This release of \dealii contains a number of large and significant changes
that will be discussed in this section.
It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}{
in the file that lists all changes for this release}, see \cite{changes91}.

@@

Previously, all triangulation classes of \texttt{deal.II} had in common that the coarse grid is replicated by
all processes in a parallel environment, and the actual mesh used for computations is constructed by repeated
refinement. However, this has its limitations in many
applications where the mesh comes
from an external mesh generator in the form of a file that frequently
already contains millions
or tens of millions of cells. For such configurations, applications might exhaust
available memory already while reading the mesh on each MPI process.

@@

Since the previous release, \dealii has had support for $hp$-adaptive finite element methods
on distributed memory systems \cite{dealII91}. We implemented the bare functionality
for $hp$-adaptive methods with the objective to offer the greatest flexibility in
their application. Here, reference finite elements still had to be assigned manually
to each cell, which may not lead to an optimal mesh and is tedious.

@@

The class \texttt{VectorizedArray<Number>} is a key component to achieve the high
node-level performance of the matrix-free algorithms in deal.II~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper
class around a short vector of $n$ entries of type \texttt{Number} and maps
arithmetic operations to appropriate single-instruction/multiple-data (SIMD)
concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this release by making
it compatible with the STL algorithms found in the header \texttt{<algorithm>}.
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}.
Furthermore, the \texttt{VectorizedArray} class now supports range-based iteration over its entries.

In previous \dealii{} releases, the
vector length was set at compile time of the library to match the highest
value supported by the given processor architecture.
Now, a second optional template argument
can be specified as \texttt{VectorizedArray<Number, size>}, where \texttt{size} explicitly controls
the vector length within the capabilities of a particular instruction set.
(A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.)
This allows users to select the vector length/ISA and,
as a consequence, the number of cells to be processed at once in matrix-free
operator evaluations. For example, the deal.II-based
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order
discontinuous Galerkin methods (with more than a thousand degrees of freedom per cell), constructs a tensor product of two \texttt{MatrixFree} objects of different SIMD-vector
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

@@

\caption{\it Comparison of relevant SIMD-related classes in deal.II and \texttt{C++23}.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (\texttt{C++23})} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

The new interface of \texttt{VectorizedArray} also enables replacement
by any type with a matching interface. Specifically, this prepares
\dealii{} for the \texttt{std::simd} class that is slated to become
part of the \texttt{C++23} standard.
Table~\ref{tab:simd} compares the deal.II-specific SIMD classes and
the equivalent \texttt{C++23} classes. These changes also prepare for specialized
code paths exploiting
vectorization within an element, see~\cite{KronbichlerKormann2019}.

@@

%Further additions to the \texttt{MatrixFree} infrastructure consist of:
%\begin{itemize}
%\item a new variant of \texttt{MatrixFree::cell\_loop()}: It takes two
%\texttt{std::function} objects with ranges on the locally owned degrees of freedom, one
%with work to be scheduled before the cell operation first touches some
%unknowns and another with work to be executed after the cell operation last
%touches them. The goal of
%these functions is to bring vector operations close to the time when the
%vector entries are accessed by the cell operation, which increases the cache
%hit rate of modern processors by improved temporal locality.
%\item a new form of loop \texttt{MatrixFree::loop\_cell\_centric()}: This
%kind of loop can be used in the context of discontinuous Galerkin methods,
%where both cell and face integrals have to be evaluated. While in the case of
%the traditional \texttt{loop}, cell and face integrals have been performed
%independently, the new loop performs all cell and face integrals of a cell in
%one go. This includes that each face integral has to be evaluated twice, but
%entries have to be written into the solution vector only once with improved
%data locality. Previous publications based on \texttt{deal.II} have shown the
%relevance of the latter aspect for reaching higher performance.
%\end{itemize}

@@

  The $C^0$IP approach is a modern alternative to classical methods that
  use $C^1$-conforming elements such as the Argyris
  element, the Clough-Tocher element and others, all developed in the
  late 1960s. From a twenty-first century perspective, they can only be
  described as bizarre in their construction. They are also exceedingly
  cumbersome to implement if one wants to use general meshes. As a
  consequence, they have largely fallen out of favor and deal.II currently
  does not contain implementations of these shape functions.

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subsection~\ref{subsec:performance}, deal.II by default no longer
stores information for all processes on all processes, but only
local or locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling
\texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.

@@

In order to justify the work the developers of \dealii put into this
software, we ask that papers using the library reference one of the
\dealii papers. This helps us justify the effort we put into it.

There are various ways to reference \dealii. To acknowledge the use of
the current version of the library, \textbf{please reference the present
document}. For up to date information and a bibtex entry
see
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
   \vfill\null  \columnbreak
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For boundary element computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
 \item For uses of the \texttt{ParameterAcceptor} concept, the
   \texttt{MeshWorker::ScratchData} base class, and the
   \texttt{ParsedConvergenceTable} class:
   \cite{SartoriGiulianiBardelloni-2018-a};
 \item For uses of the particle functionality in \dealii{}:
   \cite{GLHPB18}.
   \vfill\null  
\end{itemize}
\end{multicols}

\dealii can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item Ginkgo \cite{ginkgo-web-page}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
  %
  % nanoflann has been deprecated and will be removed for 9.3. remove
  % this line in the 9.3 release paper
  %
\item NetCDF \cite{rew1990netcdf}
  %
  % netcdf has been deprecated and will be removed for 9.3. remove
  % this line in the 9.3 release paper
  %
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item SymEngine \cite{symengine-web-page}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

The two previous releases of \dealii can be cited as
\cite{dealII90,dealII91}.

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

\dealii and its developers are financially supported through a
variety of funding sources:

@@

The Interdisciplinary Center for Scientific Computing (IWR) at Heidelberg
University has provided hosting services for the \dealii web page.

>>>>

\title{The \dealii{} Library, Version 9.2}

@@

\dealii{} version 9.2.0 was released May XYZ, 2020.
\todo[inline]{Need to update date.}
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii{} software library version 9.2. \dealii{} is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

This release of \dealii{} contains a number of large and significant changes
that will be discussed in this section.
It of course also contains a
vast number of smaller changes and added functionality; the details of these
can be found
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_0_1_and_9_1_0.html}{
in the file that lists all changes for this release}, see \cite{changes91}.

@@

Previously, all triangulation classes of \dealii{} had in common that the coarse grid is replicated by
all processes in a parallel environment, and the actual mesh used for computations is constructed by repeated
refinement. However, this has its limitations in many
applications where the mesh comes
from an external mesh generator in the form of a file that frequently
already contains millions
or tens of millions of cells. For such configurations, applications might exhaust
available memory already while reading the mesh on each MPI process.

@@

Since the previous release, \dealii{} has had support for $hp$-adaptive finite element methods
on distributed memory systems \cite{dealII91}. We implemented the bare functionality
for $hp$-adaptive methods with the objective to offer the greatest flexibility in
their application. Here, reference finite elements still had to be assigned manually
to each cell, which may not lead to an optimal mesh and is tedious.

@@

The class \texttt{VectorizedArray<Number>} is a key component to achieve the high
node-level performance of the matrix-free algorithms in \dealii{}~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper
class around a short vector of $n$ entries of type \texttt{Number} and maps
arithmetic operations to appropriate single-instruction/multiple-data (SIMD)
concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this release by making
it compatible with the STL algorithms found in the header \texttt{<algorithm>}.
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}.
Furthermore, the \texttt{VectorizedArray} class now supports range-based iteration over its entries.

In previous \dealii{} releases, the
vector length was set at compile time of the library to match the highest
value supported by the given processor architecture.
Now, a second optional template argument
can be specified as \texttt{VectorizedArray<Number, size>}, where \texttt{size} explicitly controls
the vector length within the capabilities of a particular instruction set.
(A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.)
This allows users to select the vector length/ISA and,
as a consequence, the number of cells to be processed at once in matrix-free
operator evaluations. For example, the \dealii{}-based
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order
discontinuous Galerkin methods (with more than a thousand degrees of freedom per cell), constructs a tensor product of two \texttt{MatrixFree} objects of different SIMD-vector
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

@@

\caption{\it Comparison of relevant SIMD-related classes in \dealii{} and \texttt{C++23}.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (\dealii{})} & \textbf{std::simd (\texttt{C++23})} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

The new interface of \texttt{VectorizedArray} also enables replacement
by any type with a matching interface. Specifically, this prepares
\dealii{} for the \texttt{std::simd} class that is slated to become
part of the \texttt{C++23} standard.
Table~\ref{tab:simd} compares the \dealii{}-specific SIMD classes and
the equivalent \texttt{C++23} classes. These changes also prepare for specialized
code paths exploiting
vectorization within an element, see~\cite{KronbichlerKormann2019}.

@@

%Further additions to the \texttt{MatrixFree} infrastructure consist of:
%\begin{itemize}
%\item a new variant of \texttt{MatrixFree::cell\_loop()}: It takes two
%\texttt{std::function} objects with ranges on the locally owned degrees of freedom, one
%with work to be scheduled before the cell operation first touches some
%unknowns and another with work to be executed after the cell operation last
%touches them. The goal of
%these functions is to bring vector operations close to the time when the
%vector entries are accessed by the cell operation, which increases the cache
%hit rate of modern processors by improved temporal locality.
%\item a new form of loop \texttt{MatrixFree::loop\_cell\_centric()}: This
%kind of loop can be used in the context of discontinuous Galerkin methods,
%where both cell and face integrals have to be evaluated. While in the case of
%the traditional \texttt{loop}, cell and face integrals have been performed
%independently, the new loop performs all cell and face integrals of a cell in
%one go. This includes that each face integral has to be evaluated twice, but
%entries have to be written into the solution vector only once with improved
%data locality. Previous publications based on \dealii{} have shown the
%relevance of the latter aspect for reaching higher performance.
%\end{itemize}

@@

  The $C^0$IP approach is a modern alternative to classical methods that
  use $C^1$-conforming elements such as the Argyris
  element, the Clough-Tocher element and others, all developed in the
  late 1960s. From a twenty-first century perspective, they can only be
  described as bizarre in their construction. They are also exceedingly
  cumbersome to implement if one wants to use general meshes. As a
  consequence, they have largely fallen out of favor and \dealii{} currently
  does not contain implementations of these shape functions.

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subection~\ref{subsec:performance}, \dealii{} by default no longer
stores information for all processes on all processes, but only
local or locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling
\texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.

@@

In order to justify the work the developers of \dealii{} put into this
software, we ask that papers using the library reference one of the
\dealii{} papers. This helps us justify the effort we put into it.

There are various ways to reference \dealii{}. To acknowledge the use of
the current version of the library, \textbf{please reference the present
document}. For up to date information and a bibtex entry
see
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}

The original \dealii{} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
   \vfill\null  \columnbreak
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For boundary element computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
 \item For uses of the \texttt{ParameterAcceptor} concept, the
   \texttt{MeshWorker::ScratchData} base class, and the
   \texttt{ParsedConvergenceTable} class:
   \cite{SartoriGiulianiBardelloni-2018-a};
 \item For uses of the particle functionality in \dealii{}:
   \cite{GLHPB18}.
   \vfill\null  
\end{itemize}
\end{multicols}

\dealii{} can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\begin{multicols}{3}
\begin{itemize}
\item ADOL-C \cite{Griewank1996a,adol-c}
\item ARPACK \cite{arpack}
\item Assimp \cite{assimp}
\item BLAS and LAPACK \cite{lapack}
\item cuSOLVER \cite{cusolver}
\item cuSPARSE \cite{cusparse}
\item Gmsh \cite{geuzaine2009gmsh}
\item GSL \cite{gsl2016}
\item Ginkgo \cite{ginkgo-web-page}
\item HDF5 \cite{hdf5}
\item METIS \cite{karypis1998fast}
\item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
\item muparser \cite{muparser-web-page}
\item nanoflann \cite{nanoflann}
  %
  % nanoflann has been deprecated and will be removed for 9.3. remove
  % this line in the 9.3 release paper
  %
\item NetCDF \cite{rew1990netcdf}
  %
  % netcdf has been deprecated and will be removed for 9.3. remove
  % this line in the 9.3 release paper
  %
\item OpenCASCADE \cite{opencascade-web-page}
\item p4est \cite{p4est}
\item PETSc \cite{petsc-user-ref,petsc-web-page}
\item ROL \cite{ridzal2014rapid}
\item ScaLAPACK \cite{slug}
\item SLEPc \cite{Hernandez:2005:SSF}
\item SUNDIALS \cite{sundials}
\item SymEngine \cite{symengine-web-page}
\item TBB \cite{Rei07}
\item Trilinos \cite{trilinos,trilinos-web-page}
\item UMFPACK \cite{umfpack}
\end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

The two previous releases of \dealii{} can be cited as
\cite{dealII90,dealII91}.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

\dealii{} and its developers are financially supported through a
variety of funding sources:

@@

The Interdisciplinary Center for Scientific Computing (IWR) at Heidelberg
University has provided hosting services for the \dealii{} web page.
